\documentclass[10pt]{article}
\usepackage[a4paper,top=2.54cm,bottom=4.94cm,left=1.93cm,right=1.93cm]{geometry}
\usepackage{times}
\usepackage{amsmath,amsfonts}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\floatstyle{plain}
\newfloat{algorithm}{tbp}{loa}
\floatname{algorithm}{Algorithm}

\setlength{\parskip}{0pt}
\setlength{\parindent}{1.5em}
\pagestyle{empty}
\linespread{1.0}
\renewcommand{\texttt}[1]{\textnormal{#1}}
\renewcommand{\path}[1]{\textnormal{#1}}

\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}
  {1.5ex plus 0.5ex minus 0.2ex}
  {1.2ex}
  {\normalfont\bfseries\centering\fontsize{11pt}{13pt}\selectfont}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}
  {1.2ex plus 0.3ex minus 0.1ex}
  {0.8ex}
  {\normalfont\bfseries\fontsize{10pt}{12pt}\selectfont}}
\renewcommand\@seccntformat[1]{\csname the#1\endcsname.\quad}
\makeatother

\renewcommand{\refname}{REFERENCES}

\begin{document}
\thispagestyle{empty}

\begin{center}
{\fontsize{16pt}{18pt}\selectfont\bfseries
RoPINN-ResFF: Task-Conditional Enhancement of Region-Optimized PINNs with Residual Fourier Features\par}
\vspace{0.9em}
{\fontsize{12pt}{14pt}\selectfont
Author One$^{a,*}$, Author Two$^{b}$\par}
\vspace{0.5em}
{\fontsize{12pt}{14pt}\selectfont
$^{a}$School/Institute Name, City, Postal Code, Country\par
$^{b}$School/Institute Name, City, Postal Code, Country\par
$^{*}$Corresponding author: your-email@domain.com\par}
\end{center}

\vspace{0.8em}
\begin{center}
{\fontsize{11pt}{13pt}\selectfont\bfseries ABSTRACT}
\end{center}
\noindent
Physics-informed neural networks (PINNs) provide a mesh-free framework for solving PDEs, yet they often exhibit spectral bias and optimization instability under finite collocation sampling. RoPINN partially alleviates this issue by enforcing PDE constraints over local neighborhoods rather than isolated points. We present RoPINN-ResFF, an architecture-level extension of RoPINN that combines a residual multilayer perceptron backbone with fixed random Fourier feature embedding. Under a fixed budget of 1000 iterations, we report paired multi-seed results on reaction, wave, and convection benchmarks (reaction: 11 seeds; wave/convection: 5 seeds). We treat reaction as the confirmatory task and wave/convection as transfer-oriented directional evaluations under lower compute. On reaction, mean relative L1/L2 decrease from 0.204406/0.223945 (baseline) to 0.003313/0.008480 (ours), with exact paired randomization p-values of 0.00098 for both metrics. On wave, mean L1/L2 decrease from 0.060335/0.062967 to 0.011916/0.012183. On convection, mean L1/L2 increase from 0.619487/0.699839 to 1.015963/1.039029. To assess budget sensitivity, we additionally run reaction at 3000 and 5000 iterations (3 paired seeds), where improvements remain stable (L1/L2 reductions: 88.53\%/84.28\% at 3000 and 88.64\%/84.44\% at 5000). A capacity-matched reaction control (1,643,481-parameter PINN vs. 1,642,497-parameter RoPINN-ResFF) still shows strong gains for RoPINN-ResFF (L1: 0.001947 vs. 0.037791; L2: 0.004269 vs. 0.070529), indicating that improvements are not explained by model size alone. Overall, the empirical evidence supports a task-conditional conclusion rather than universal gains across PDE types.

\vspace{0.5em}
\noindent\textbf{Keywords:} physics-informed neural networks, RoPINN, Fourier features, PDE solver, region optimization.

\input{sections/intro}
\input{sections/related}
\input{sections/method}
\input{sections/experiments}
\input{sections/discussion}
\input{sections/conclusion}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
